---
title: "Cleaning Script"
output: github_document
date: "Last Updated: February 24, 2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Loading

```{r}
library(ggpubr)
library(ggsignif)
library(maps)
library(pheatmap)
library(RColorBrewer)
library(rnaturalearth)
library(rnaturalearthhires)
library(sf)
library(tidyverse)
library(viridis)
```

## Data Loading 

```{r}
survey_data <- read.csv("/Users/kenjinchang/github/stakeholder-analysis/data/parent-files/survey-data.csv")
extraction_data <- read.csv("/Users/kenjinchang/github/stakeholder-analysis/data/parent-files/extraction-data.csv")
```

## Data Cleaning: Scoping Review

* `study_id`: the unique numeral identifier assigned to each independently eligible study included within our scoping review (1-116).
* `study`: the parenthetical, in-text citation for each independently eligible study's corresponding record of reference. 
* `study_no`: the assigned number specifying the order in which the independently eligible study appears within the corresponding record of reference.
* `study_count`: the total number of independently eligible studies appearing within the corresponding record of reference.
* `doi`: the handle, or digital object identifier (DOI), assigned to each independently eligible study's corresponding record of reference.
* `pub_year`: the calendar year when each independently eligible study's corresponding record of reference was published (2001-2024).
* `pub_title`: the given title for each independently eligible study's corresponding record of reference.
* `pub_journal`: the publishing journal of each independently eligible study's record of reference.
* `university_list`: the complete list of treatment-receiving universities participating in the independently eligible study.
* `university_count`: the total number of treatment-receiving universities participating in the independently eligible study.
* `investigation_cat`: the scale of the independently eligible study's investigation (single-site for study's localized to one treatment-receiving university or multi-site for study's implemented across multiple treatment-receiving universities).
* `nation_list`: a duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the ISO (International Organization for Standardization) countries in which they are located.
* `nation_list_count`: the total number of unique and duplicate ISO countries associated with the participating treatment-receiving universities mentioned in each study.
* `nation_var`: a non-duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the ISO countries in which they are located.
* `nation_var_count`: the total number of unique ISO countries associated with the participating treatment-receiving universities mentioned in each study.
* `us_state_list`: a conditional, duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.S. state in which they are located.
* `us_state_list_count`: the total number of unique and duplicate U.S. states associated with the participating treatment-receiving universities mentioned in each study.
* `us_state_var`: a conditional, non-duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.S. states in which they are located.
* `us_state_var_count`: the total number of unique U.S. states associated with the participating treatment-receiving universities mentioned in each study. 
* `uk_country_list`: a conditional, duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.K. country in which they are located.
* `uk_country_list_count`: the total number of unique and duplicate U.K. countries associated with the participating treatment-receiving universities mentioned each study.
* `uk_country_var`: a conditional, non-duplicate allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.K. countries in which they are located.
* `uk_country_var_count`: the total number of unique U.K. countries associated with the participating treatment-receiving universities mentioned in each study.
* `strategy_list`: a duplicate-allowing list pairing the reported intervention components mentioned in each study with the specific behavioral strategies being leveraged. 
* `approach_cat`: the diagnosed behavioral approach associated with each study, based on the strategies mapping on to each study's reported intervention components.
* `target_list`: a duplicate-allowing list pairing the reported intervention components mentioned in each study with the specific socio-ecological tiers being targeted.
* `breadth_cat`: the diagnosed breadth of change associated each study, based on the socio-ecological tiers mapping on to each study's reported intervention components.
* `design`: the  research design of the included study, as determined by the nature of comparison being made (between, within, or between and within).
* `principal_indicator_list`: a duplicate-allowing list outlining the primary outcome measures being used to document changes to food selection or food service in response to the study's reported intervention. 
* `principal_indicator_list_count`: the total number of unique and duplicate primary outcome measures being
* `principal_indicator_var`:
* `principal_indicator_var_count`:
* `accessory_indicator_list`:
* `accessory_indicator_list_count`:
* `accessory_indicator_var`:
* `accessory_indicator_var_count`:
* `qualifying_indicator_list`:
* `qualifying_indicator_list_count`:
* `qualifying_indicator_var`:
* `qualifying_indicator_var_count`:
* `spillover_monitoring_list`:
* `spillover_monitoring_list_count`:
* `spillover_monitoring_var`:
* `spillover_monitoring_var_count`:
* `intention_behavior_monitoring`:

### Time

```{r}
temporal_frequencies <- extraction_data %>%
  select(pub_year,university_count) %>%
  drop_na() %>%
  mutate(count=case_when(university_count>=1~1)) %>%
  group_by(pub_year) %>%
  summarise(frequency=sum(count)) %>%
  mutate(cumulative_frequency=cumsum(frequency)) %>%
  add_row(pub_year=2000,frequency=0) %>%
  add_row(pub_year=2002,frequency=0) %>%
  add_row(pub_year=2003,frequency=0) %>%
  add_row(pub_year=2004,frequency=0) %>%
  add_row(pub_year=2007,frequency=0) %>%
  add_row(pub_year=2008,frequency=0) %>%
  add_row(pub_year=2010,frequency=0) %>%
  arrange(pub_year) %>%
  mutate(cumulative_frequency=cumsum(frequency)) 
temporal_frequencies
```

```{r}
exponential_fit <- temporal_frequencies %>%
  slice(-1)
exponential_model <- lm(log(cumulative_frequency)~pub_year,data=exponential_fit)
summary(exponential_model)
```

```{r}
temporal_frequencies_plot <- temporal_frequencies %>%
  ggplot(aes(x=pub_year,y=frequency,color=frequency,fill=frequency)) + 
  geom_col() +
  scale_fill_gradient(name="Count",low="lavender",high="lightslateblue",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  scale_color_gradient(name="Count",low="lavender",high="lightslateblue",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  xlab("Publication Year") + 
  ylab("Frequency") + 
  scale_y_continuous(limits=c(0,120)) +
  scale_x_continuous(breaks=c(2000,2004,2008,2012,2016,2020,2024),limits=c(2000,2025)) +
  labs(caption="   ") + 
  theme(legend.position="none",legend.justification="center",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
temporal_cumulative_frequencies_plot <- temporal_frequencies %>%
  ggplot(aes(x=pub_year,y=cumulative_frequency,color=cumulative_frequency,fill=cumulative_frequency)) +
  scale_fill_gradient(name="Count",low="lavender",high="lightslateblue",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  scale_color_gradient(name="Count",low="lavender",high="lightslateblue",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  geom_col() + 
  xlab("Publication Year") + 
  ylab("Cumulative Frequency") + 
  scale_y_continuous(limits=c(0,120)) +
  scale_x_continuous(breaks=c(2000,2004,2008,2012,2016,2020,2024),limits=c(2000,2025)) +
  labs(caption="Adjusted R-Squared: 0.985 (3sf); p-value < 0.001") + 
  theme(legend.title.position="none",legend.position="none",legend.justification="center",legend.box.spacing=unit(0,"pt"),legend.key.width=unit(50,"pt"),legend.key.height=unit(7.5,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
temporal_plots <- ggarrange(temporal_frequencies_plot,temporal_cumulative_frequencies_plot,
          nrow=2,
          labels=c("A","B"))
ggsave(filename="publication-rate.png",plot=temporal_plots,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=40,height=30,units="cm",dpi=150,limitsize=TRUE)
temporal_plots
```

### Place

```{r}
global_shapefile <- map_data("world")
global_shapefile <- global_shapefile %>% 
  rename(country=region) %>%
  mutate(country=case_when(country=="Macedonia"~"North Macedonia",
                           country=="Ivory Coast"~"Cote d'Ivoire",
                           country=="Democratic Republic of the Congo"~"Congo, Dem. Rep.",
                           country=="Republic of Congo"~"Congo, Rep.",
                           country=="UK"~"United Kingdom",
                           country=="USA"~"United States",
                           country=="Laos"~"Lao",
                           country=="Slovakia"~"Slovak Republic",
                           country=="Saint Lucia"~"St. Lucia",
                           country=="Kyrgyzstan"~"Krygyz Republic",
                           country=="Micronesia"~"Micronesia, Fed. Sts.",
                           country=="Swaziland"~"Eswatini",
                           country=="Virgin Islands"~"Virgin Islands (U.S.)",
                        TRUE~country))
island_nations <- c("Antigua","Barbuda","Nevis", 
                 "Saint Kitts","Trinidad",
                 "Tobago","Grenadines","Saint Vincent")
island_nations_match <- global_shapefile %>% 
  filter(country %in% island_nations)
ant_bar <- c(137,138 )
kit_nev <- c(930,931)
tri_tog <- c(1425,1426)
vin_gre <- c(1575,1576,1577)
island_nation_names <- c("Antigua and Barbuda","St. Kitts and Nevis","Trinidad and Tobago","St. Vincent and the Grenadines")
island_nations_match <- island_nations_match %>% 
  mutate(country=case_when(group %in% ant_bar~"Antigua and Barbuda",
                           group %in% kit_nev~"St. Kitts and Nevis",
                           group %in% tri_tog~"Trinidad and Tobago",
                           group %in% vin_gre~"St. Vincent and the Grenadines")) %>% 
  tibble()
global_shapefile <- global_shapefile %>%
  filter(!country %in% island_nation_names)
global_shapefile <- global_shapefile %>% 
  bind_rows(island_nations_match) %>%
  arrange(country) %>%
  tibble()
sra_names <- c("Hong Kong","Macao")
hk_mc <- global_shapefile %>% 
  filter(subregion %in% sra_names)
hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion=="Hong Kong"~"Hong Kong, China",
                             subregion=="Macao"~"Macao, China"))
global_shapefile <- global_shapefile %>%
  filter(!subregion %in% sra_names)
global_shapefile <- global_shapefile %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

```{r}
spatial_frequencies <- extraction_data %>%
  select(nation_var,nation_var_count) %>%
  rename(country=nation_var) %>%
  mutate(across(country,str_replace,"USA","United States")) %>%
  mutate(across(country,str_replace,"UK","United Kingdom")) %>%
  group_by(country) %>%
  summarise(frequency=sum(nation_var_count)) %>%
  arrange(desc(frequency))
spatial_frequencies
```

```{r}
spatial_frequencies %>%
  summarise(sum(frequency))
```
scale_fill_gradient(low='white', high='grey20', limits=c(1, 10))

scale_fill_gradient(low="lavender",high="slateblue4",na.value="white",name="Intervention-Receiving Institutions",guide=guide_colourbar(reverse=FALSE,title.position="top",title.hjust=0.5,limits=c(1,116))) +

```{r}
crs_robin <- "+proj=robin +lat_0=0 +lon_0=0 +x0=0 +y0=0"
```


```{r}
spatial_frequencies_joined <- left_join(global_shapefile,spatial_frequencies,by="country")
national_frequencies <- spatial_frequencies_joined %>%
  ggplot(aes(x=long,y=lat,fill=frequency,group=group)) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_gradient(low="lavender",high="lightslateblue",na.value="white",limits=c(0,55),breaks=c(0,11,22,33,44,55)) +
  coord_sf(crs=crs_robin) +
  xlab("") + 
  ylab("") +
  scale_y_continuous(limits=c(-55,85)) +
  labs(fill="Frequency") +
  theme(aspect.ratio=.48,legend.position="bottom",legend.title.position="top",legend.box.spacing=unit(-10,"pt"),legend.key.width=unit(100,"pt"),legend.key.height=unit(5,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="aliceblue"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
usa_shapefile <- map_data("county") %>%
  rename(state=region)
```

```{r}
state_frequencies <- extraction_data %>%
  select(study,us_state_var) %>%
  separate_longer_delim(c(us_state_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(us_state_var) %>%
  summarise(frequency=sum(count)) %>%
  arrange(desc(frequency)) %>%
  mutate(us_state_var=tolower(us_state_var)) %>%
  rename(state=us_state_var) %>%
  drop_na()
state_frequencies 
```

```{r}
state_frequencies %>% summarise(sum(frequency))
```

```{r}
state_frequencies_joined <- left_join(usa_shapefile,state_frequencies,by="state")
```

```{r}
usa_frequencies <- state_frequencies_joined %>%
  ggplot(aes(x=long,y=lat,fill=frequency,group=group)) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_gradient(low="lavender",high="lightslateblue",na.value="white",limits=c(1,55)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  coord_map("albers",lat0=45.5,lat1=29.5) +
  theme(legend.key.width=unit(3,"lines"),legend.position="none",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="aliceblue"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
subnational_frequencies <- extraction_data %>%
  select(uk_country_var,uk_country_var_count) %>%
  rename(subregion=uk_country_var) %>%
  separate_longer_delim(c(subregion,uk_country_var_count),delim=";") %>%
  mutate(uk_country_var_count=as.numeric(uk_country_var_count)) %>%
  group_by(subregion) %>%
  summarise(frequency=sum(uk_country_var_count)) %>%
  arrange(desc(frequency)) %>%
  mutate(across("subregion",str_replace,"England","Great Britain")) %>%
  drop_na()
subnational_frequencies
```

```{r}
uk_shapefile <- ne_states(country="united kingdom",returnclass="sf")
```

```{r}
subnational_frequencies <- subnational_frequencies %>%
  mutate(across('subregion',str_replace,"Great Britain","England")) %>%
  rename(geonunit=subregion)
subnational_frequencies
```

```{r}
subnational_frequencies_joined <- left_join(uk_shapefile,subnational_frequencies,by="geonunit")
```

```{r}
uk_frequencies <- subnational_frequencies_joined %>%
ggplot(aes(fill=frequency,group=geonunit)) + 
  geom_sf(aes(fill=frequency),color="black",linewidth=0.125) +
  scale_fill_gradient(low="lavender",high="lightslateblue",na.value="white",limits=c(1,55)) +
  theme(legend.key.width=unit(3,"lines"),legend.position="none",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="aliceblue"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
subnational_frequency_choros <- ggarrange(usa_frequencies,uk_frequencies,
                                         ncol=2,
                                         labels=c("B","C"))
national_frequency_choros <- ggarrange(national_frequencies,
                                       labels="A")
```


```{r}
spatial_plots <- ggarrange(national_frequency_choros,subnational_frequency_choros,
          nrow=2)
ggsave(filename="publication-distribution.png",plot=spatial_plots,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=40,height=40,units="cm",dpi=150,limitsize=TRUE)
spatial_plots
```

### Primary Performance Indicators

```{r}
ppi_frequencies <- extraction_data %>%
  select(study,principal_indicator_var) %>%
  separate_longer_delim(c(principal_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(principal_indicator_var) %>%
  summarise(frequency=sum(count)) %>%
  mutate(across(principal_indicator_var,str_replace_all,"Observed Food Choice","Food Choice, Observed")) %>%
  mutate(across(principal_indicator_var,str_replace_all,"Observed Food Service","Food Service, Observed")) %>%
  mutate(across(principal_indicator_var,str_replace_all,"Self-Reported Food Choice","Food Choice, Self-Reported")) %>%
  mutate(across(principal_indicator_var,str_replace_all,"Intended Food Choice","Food Choice, Intended")) 
ppi_frequencies 
```

```{r}
principal_indicator_var_manual <- c("Food Choice, Intended","Food Choice, Self-Reported","Food Choice, Observed","Food Service, Observed")
frequency_manual <- c(36,67,54,2)
ppi_frequencies_manual <- tibble(principal_indicator_var_manual,frequency_manual) %>%
  arrange(desc(frequency_manual))
ppi_frequencies_manual 
```

```{r}
ppi_contingency_table <- ppi_frequencies_manual %>%
  rename(Reported=frequency_manual) %>%
  mutate(Omitted=116-Reported)
ppi_contingency_table
```

```{r}
ppi_contigency_table <- as.table(rbind(c(67,54,36,2),c(49,62,80,114)))
dimnames(ppi_contigency_table) <- list(dichotomy=c("Reported","Omitted"),
                                       indicators=c("Food Choice, Self-Reported","Food Choice, Observed","Food Choice, Intended","Food Service, Observed"))
ppi_chisq_test <- chisq.test(ppi_contigency_table)
ppi_chisq_test
```
Significant associated between the type of principal performance indicator and its likelihood of appearance

```{r}
ppi_observed_counts <- ppi_chisq_test$observed
print(ppi_chisq_test)
```

```{r}
ppi_expected_counts <- ppi_chisq_test$expected
print(round(ppi_expected_counts,2))
```

```{r}
ppi_pearson_residuals <- ppi_chisq_test$residuals
print(round(ppi_pearson_residuals,2))
```

```{r}
ppi_contributions <- (ppi_observed_counts-ppi_expected_counts)^2/ppi_expected_counts
ppi_total_chi_square <- ppi_chisq_test$statistic
ppi_percentage_contributions <- 100*ppi_contributions/ppi_total_chi_square
print("Percentage Contributions:")
```

```{r}
print(round(ppi_percentage_contributions,2))
```

```{r}
pheatmap(ppi_percentage_contributions,display_numbers=TRUE,cluster_rows=FALSE,cluster_cols=FALSE,main="Percentage Contributions to Chi-Square Statistic")
```


```{r}
ppi_contingency_table_alt <- ppi_contingency_table %>%
  pivot_longer(!principal_indicator_var_manual,names_to="appearance",values_to="frequency_manual") %>%
  mutate(contribution=case_when(principal_indicator_var_manual=="Food Choice, Self-Reported"&appearance=="Reported"~20.47,
    principal_indicator_var_manual=="Food Choice, Self-Reported"&appearance=="Omitted"~10.67,
    principal_indicator_var_manual=="Food Choice, Observed"&appearance=="Reported"~5.60,
    principal_indicator_var_manual=="Food Choice, Observed"&appearance=="Omitted"~2.92,
    principal_indicator_var_manual=="Food Choice, Intended"&appearance=="Reported"~0.39,
    principal_indicator_var_manual=="Food Choice, Intended"&appearance=="Omitted"~0.20,
    principal_indicator_var_manual=="Food Service, Observed"&appearance=="Reported"~39.28,
    principal_indicator_var_manual=="Food Service, Observed"&appearance=="Omitted"~20.48)) %>%
  mutate(label_y=case_when(appearance=="Reported"~118,
                           appearance=="Omitted"~-2))
ppi_contingency_table_alt
```

```{r}
ppi_frequencies_plot <- ppi_contingency_table_alt %>%
  ggplot(aes(x=principal_indicator_var_manual,y=frequency_manual,fill=appearance,color=appearance)) + 
  geom_col() +
  geom_text(aes(y=label_y,label=paste(format(contribution,nsmall=2),"%")),color="black",size=3) +
  geom_signif(comparisons=list(c("Food Choice, Self-Reported","Food Service, Observed")),color="black",size=0.25,annotation="***",y_position=116,tip_length=0.02,vjust=0) +
  xlab("Principal Indicator") +
  ylab("Frequency") +
  scale_x_discrete(limits=c("Food Service, Observed","Food Choice, Intended","Food Choice, Observed","Food Choice, Self-Reported")) + 
  scale_y_continuous(breaks=c(0,29,58,87,116)) +
  scale_fill_manual(values=c("lavender","lightslateblue")) +
  scale_color_manual(values=c("lavender","lightslateblue")) +
  guides(fill=guide_legend(title="Mode"),color=guide_legend(title="Mode")) +
  labs(caption="X-squared: 91.3 (3sf); p-value < 0.001") + 
  theme(aspect.ratio=0.8,legend.position="right",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

### Accessory Performance Indicators

```{r}
api_frequencies <- extraction_data %>%
  select(study,accessory_indicator_var) %>%
  separate_longer_delim(c(accessory_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(accessory_indicator_var) %>%
  summarise(frequency=sum(count))
api_frequencies
```

```{r}
accessory_indicator_var_manual <- c("Campus Culture","Dietary Health","Food Pricing","Guest Dining Experience","Institutional Sustainability","Operating Costs","Staff Satisfaction","Sustainability of Guest Food Choices")
frequency_manual <- c(82,27,4,5,2,14,1,13)
api_frequencies_manual <- tibble(accessory_indicator_var_manual,frequency_manual) %>%
  arrange(desc(frequency_manual))
api_frequencies_manual 
```

```{r}
api_contigency_table <- api_frequencies_manual %>%
  rename(Reported=frequency_manual) %>%
  mutate(Omitted=116-Reported)
api_contigency_table
```

```{r}
api_contigency_table_alt <- api_contigency_table %>%
  pivot_longer(!accessory_indicator_var_manual,names_to="appearance",values_to="frequency_manual") %>%
  mutate(contribution=case_when(accessory_indicator_var_manual=="Campus Culture"&appearance=="Reported"~62.97,
    accessory_indicator_var_manual=="Campus Culture"&appearance=="Omitted"~13.71,
    accessory_indicator_var_manual=="Dietary Health"&appearance=="Reported"~0.66,
    accessory_indicator_var_manual=="Dietary Health"&appearance=="Omitted"~0.14,
    accessory_indicator_var_manual=="Operating Costs"&appearance=="Reported"~0.76,
    accessory_indicator_var_manual=="Operating Costs"&appearance=="Omitted"~0.17,
    accessory_indicator_var_manual=="Sustainability of Guest Food Choices"&appearance=="Reported"~1.00,
    accessory_indicator_var_manual=="Sustainability of Guest Food Choices"&appearance=="Omitted"~0.22,
    accessory_indicator_var_manual=="Guest Dining Experience"&appearance=="Reported"~4.15,
    accessory_indicator_var_manual=="Guest Dining Experience"&appearance=="Omitted"~0.90,
    accessory_indicator_var_manual=="Food Pricing"&appearance=="Reported"~0.16,
    accessory_indicator_var_manual=="Food Pricing"&appearance=="Omitted"~0.03,
    accessory_indicator_var_manual=="Institutional Sustainability"&appearance=="Reported"~5.89,
    accessory_indicator_var_manual=="Institutional Sustainability"&appearance=="Omitted"~1.28,
    accessory_indicator_var_manual=="Staff Satisfaction"&appearance=="Reported"~6.53,
    accessory_indicator_var_manual=="Staff Satisfaction"&appearance=="Omitted"~1.42)) %>%
  mutate(label_y=case_when(appearance=="Reported"~118,
                           appearance=="Omitted"~-2))
api_contigency_table_alt
```

```{r}
api_frequencies_plot <- api_contigency_table_alt %>%
  ggplot(aes(x=accessory_indicator_var_manual,y=frequency_manual,fill=appearance,color=appearance)) + 
  geom_col() +
  geom_text(aes(y=label_y,label=paste(format(contribution,nsmall=2),"%")),color="black",size=3) +
  geom_signif(comparisons=list(c("Campus Culture","Staff Satisfaction")),color="black",size=0.25,annotation="***",y_position=116,tip_length=0.02,vjust=0) +
  xlab("Accessory Indicator") +
  ylab("Frequency") +
  scale_x_discrete(limits=c("Staff Satisfaction","Institutional Sustainability","Food Pricing","Guest Dining Experience","Sustainability of Guest Food Choices","Operating Costs","Dietary Health","Campus Culture")) + 
  scale_y_continuous(breaks=c(0,29,58,87,116)) +
  scale_fill_manual(values=c("aliceblue","lightsteelblue")) +
  scale_color_manual(values=c("aliceblue","lightsteelblue")) +
  guides(fill=guide_legend(title="Mode"),color=guide_legend(title="Mode")) +
  labs(caption="X-squared: 287 (3sf); p-value < 0.001") + 
  theme(aspect.ratio=0.4,legend.position="right",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
api_contigency_table <- as.table(rbind(c(82,27,14,13,5,4,2,1),c(34,89,102,103,111,12,114,115)))
dimnames(api_contigency_table) <- list(dichotomy=c("Reported","Omitted"),
                                       indicators=c("Campus Culture","Dietary Health","Operating Costs","Sustainability of Guest Food Choices","Guest Dining Experience","Food Pricing","Institutional Sustainability","Staff Satisfaction"))
api_chisq_test <- chisq.test(api_contigency_table)
api_chisq_test
```

Significant association between the type of accessory performance indicator and its likelihood of appearance (chi-square test interpretation (https://www.datacamp.com/tutorial/chi-square-test-r))

```{r}
api_observed_counts <- api_chisq_test$observed
print(api_chisq_test)
```
```{r}
api_expected_counts <- api_chisq_test$expected
print(round(api_expected_counts,2))
```
```{r}
api_pearson_residuals <- api_chisq_test$residuals
print(round(api_pearson_residuals,2))
```
```{r}
api_contributions <- (api_observed_counts-api_expected_counts)^2/api_expected_counts
api_total_chi_square <- api_chisq_test$statistic
api_percentage_contributions <- 100*api_contributions/api_total_chi_square
print("Percentage Contributions:")
print(round(api_percentage_contributions,2))
```

```{r}
library(pheatmap)
pheatmap(api_percentage_contributions,display_numbers=TRUE,cluster_rows=FALSE,cluster_cols=FALSE,main="Percentage Contributions to Chi-Square Statistic")
```

Rerun this using list class instead of variety class

list

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Campus Culture")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Dietary Health")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Operating Costs")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Sustainability of Guest Food Choices")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Guest Dining Experience")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Food Pricing")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Institutional Sustainability")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Staff Satisfaction")
```

### Performance Qualifiers 

```{r}
qpi_frequencies <- extraction_data %>%
  select(study,qualifying_indicator_var) %>%
  separate_longer_delim(c(qualifying_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(qualifying_indicator_var) %>%
  summarise(frequency=sum(count))
qpi_frequencies
```

```{r}
qualifying_indicator_var_manual <- c("Demographics","Lifestyle","Program Reception","Situational")
frequency_manual <- c(87,46,39,29)
qpi_frequencies_manual <- tibble(qualifying_indicator_var_manual,frequency_manual) %>%
  arrange(desc(frequency_manual))
qpi_frequencies_manual 
```

```{r}
qpi_contingency_table <- qpi_frequencies_manual %>%
  rename(Reported=frequency_manual) %>%
  mutate(Omitted=116-Reported)
qpi_contingency_table
```


```{r}
qpi_contingency_table_alt <- qpi_contingency_table %>%
  pivot_longer(!qualifying_indicator_var_manual,names_to="appearance",values_to="frequency_manual") %>%
  mutate(contribution=case_when(qualifying_indicator_var_manual=="Demographics"&appearance=="Reported"~39.32,
    qualifying_indicator_var_manual=="Demographics"&appearance=="Omitted"~30.05,
    qualifying_indicator_var_manual=="Lifestyle"&appearance=="Reported"~0.53,
    qualifying_indicator_var_manual=="Lifestyle"&appearance=="Omitted"~0.40,
    qualifying_indicator_var_manual=="Program Reception"&appearance=="Reported"~3.68,
    qualifying_indicator_var_manual=="Program Reception"&appearance=="Omitted"~2.82,
    qualifying_indicator_var_manual=="Situational"&appearance=="Reported"~13.15,
    qualifying_indicator_var_manual=="Situational"&appearance=="Omitted"~10.05)) %>%
  mutate(label_y=case_when(appearance=="Reported"~118,
                           appearance=="Omitted"~-2))
api_contigency_table_alt
```

```{r}
qpi_frequencies_plot <- qpi_contingency_table_alt %>%
  ggplot(aes(x=qualifying_indicator_var_manual,y=frequency_manual,fill=appearance,color=appearance)) + 
  geom_col() +
  geom_text(aes(y=label_y,label=paste(format(contribution,nsmall=2),"%")),color="black",size=3) +
  geom_signif(comparisons=list(c("Demographics","Situational")),color="black",size=0.25,annotation="***",y_position=116,tip_length=0.02,vjust=0) +
  xlab("Qualifying Indicator") +
  ylab("Frequency") +
  scale_x_discrete(limits=c("Situational","Program Reception","Lifestyle","Demographics")) + 
  scale_y_continuous(breaks=c(0,29,58,87,116)) +
  scale_fill_manual(values=c("mistyrose","lightcoral")) +
  scale_color_manual(values=c("mistyrose","lightcoral")) +
  guides(fill=guide_legend(title="Mode"),color=guide_legend(title="Mode")) +
  labs(caption="X-squared: 68.35 (2dp); p-value < 0.001") + 
  theme(aspect.ratio=0.8,legend.position="right",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
qpi_contingency_table <- as.table(rbind(c(87,46,39,29),c(29,70,77,87)))
dimnames(qpi_contingency_table) <- list(dichomoty=c("Reported","Omitted"),
                                        indicators=c("Demographics","Lifestyle","Program Reception","Situational"))
qpi_chisq_test <- chisq.test(qpi_contingency_table)
qpi_chisq_test
```
Significant association between the type of qualifying performance indicator and its likelihood of appearance

```{r}
qpi_observed_counts <- qpi_chisq_test$observed
print(qpi_chisq_test)
```
```{r}
qpi_expected_counts <- qpi_chisq_test$expected
print(round(qpi_expected_counts,2))
```

```{r}
qpi_pearson_residuals <- qpi_chisq_test$residuals
print(round(qpi_pearson_residuals,2))
```
```{r}
qpi_contributions <- (qpi_observed_counts-qpi_expected_counts)^2/qpi_expected_counts
qpi_total_chi_square <- qpi_chisq_test$statistic
qpi_percentage_contributions <- 100*qpi_contributions/qpi_total_chi_square
print("Percentage Contributions:")
```

```{r}
print(round(qpi_percentage_contributions,2))
```

```{r}
pheatmap(qpi_percentage_contributions,display_numbers=TRUE,cluster_rows=FALSE,cluster_cols=FALSE,main="Percentage Contributions to Chi-Square Statistic")
```

```{r}
principal_qualifying_indicator_plots <- ggarrange(ppi_frequencies_plot,qpi_frequencies_plot,
          ncol=2,
          labels=c("A","C"))
accessory_indicator_plots <- ggarrange(api_frequencies_plot,
          labels="B")
```

```{r}
combined_indicators <- ggarrange(principal_qualifying_indicator_plots,accessory_indicator_plots,
          nrow=2)
ggsave(filename="combined-performance-indicators.png",plot=combined_indicators,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=40,height=30,units="cm",dpi=150,limitsize=TRUE)
combined_indicators
```

### Gap Monitoring

#### Spillover 

#### Intention-Behavior Asymmetries

## Data Cleaning: Stakeholder Analysis

* `date`: the 
* `completion`: the 
* `channel`: the 
* `consent`: the 
* `involvement`: the 
* `involvement_other`: the 
* `stakeholder_type`: the 
* `stakeholder_type_other`: the 
* `role_title`: the 
* `role_duration``: the 
* `dietary_health_ranking`: the 
* `dietary_sustainability_ranking`: the 
* `institutional_sustainability_ranking`: the 
* `food_pricing_ranking`: the 
* `operating_costs_ranking`: the 
* `guest_experience_ranking`: the 
* `staff_satisfaction_ranking`: the 
* `campus_culture_ranking`: the 
* `other_ranking`: the 
* `other_ranking_other`: the 

```{r}
survey_data <- survey_data %>%
  select(RecordedDate,Progress,DistributionChannel,Q1,Q2,Q2_4_TEXT,Q6,Q6_10_TEXT,Q3,Q5_1,Q2_1,Q2_2,Q2_3,Q2_4,Q2_5,Q2_6,Q2_7,Q2_8,Q2_9,Q2_9_TEXT) %>%
  rename(date=RecordedDate,completion=Progress,mode=DistributionChannel,consent=Q1,role=Q2,role_other=Q2_4_TEXT,stakeholder_type=Q6,stakeholder_type_other=Q6_10_TEXT,position_title=Q3,position_duration=Q5_1,dietary_health_ranking=Q2_1,dietary_sustainability_ranking=Q2_2,institutional_sustainability_ranking=Q2_3,food_pricing_ranking=Q2_4,operating_costs_ranking=Q2_5,guest_experience_ranking=Q2_6,staff_satisfaction_ranking=Q2_7,campus_culture_ranking=Q2_8,other_ranking=Q2_9,other_ranking_other=Q2_9_TEXT) %>%
  slice(3:n()) %>%
  mutate(dietary_health_ranking=as.numeric(dietary_health_ranking)) %>%
  mutate(dietary_sustainability_ranking=as.numeric(dietary_sustainability_ranking)) %>%
  mutate(institutional_sustainability_ranking=as.numeric(institutional_sustainability_ranking)) %>%
  mutate(food_pricing_ranking=as.numeric(food_pricing_ranking)) %>%
  mutate(operating_costs_ranking=as.numeric(operating_costs_ranking)) %>%
  mutate(guest_experience_ranking=as.numeric(guest_experience_ranking)) %>%
  mutate(staff_satisfaction_ranking=as.numeric(staff_satisfaction_ranking)) %>%
  mutate(campus_culture_ranking=as.numeric(campus_culture_ranking)) %>%
  mutate(other_ranking=as.numeric(other_ranking)) %>%
  mutate(id=row_number(),.before=role) %>%
  mutate(campus_culture_ranking=case_when(id==22~8,TRUE~campus_culture_ranking)) %>%
  mutate(staff_satisfaction_ranking=case_when(id==22~7,TRUE~staff_satisfaction_ranking)) %>%
  mutate(operating_costs_ranking=case_when(id==22~2,TRUE~operating_costs_ranking)) %>%
  mutate(food_pricing_ranking=case_when(id==22~3,TRUE~food_pricing_ranking)) %>%
  mutate(institutional_sustainability_ranking=case_when(id==22~4,TRUE~institutional_sustainability_ranking)) %>%
  mutate(dietary_sustainability_ranking=case_when(id==22~5,TRUE~dietary_sustainability_ranking)) %>%
  mutate(dietary_health_ranking=case_when(id==22~6,TRUE~dietary_health_ranking)) %>%
  select(-other_ranking,-other_ranking_other,-completion,-date,-mode,-consent) %>%
  mutate(dietary_health_score=case_when(dietary_health_ranking==1~8,
                                        dietary_health_ranking==2~7,
                                        dietary_health_ranking==3~6,
                                        dietary_health_ranking==4~5,
                                        dietary_health_ranking==5~4,
                                        dietary_health_ranking==6~3,
                                        dietary_health_ranking==7~2,
                                        dietary_health_ranking==8~1)) %>%
  mutate(dietary_sustainability_score=case_when(dietary_sustainability_ranking==1~8,
                                                dietary_sustainability_ranking==2~7,
                                                dietary_sustainability_ranking==3~6,
                                                dietary_sustainability_ranking==4~5,
                                                dietary_sustainability_ranking==5~4,
                                                dietary_sustainability_ranking==6~3,
                                                dietary_sustainability_ranking==7~2,
                                                dietary_sustainability_ranking==8~1)) %>%
  mutate(institutional_sustainability_score=case_when(institutional_sustainability_ranking==1~8,
                                                      institutional_sustainability_ranking==2~7,
                                                      institutional_sustainability_ranking==3~6,
                                                      institutional_sustainability_ranking==4~5,
                                                      institutional_sustainability_ranking==5~4,
                                                      institutional_sustainability_ranking==6~3,
                                                      institutional_sustainability_ranking==7~2,
                                                      institutional_sustainability_ranking==8~1)) %>%
  mutate(food_pricing_score=case_when(food_pricing_ranking==1~8,
                                      food_pricing_ranking==2~7,
                                      food_pricing_ranking==3~6,
                                      food_pricing_ranking==4~5,
                                      food_pricing_ranking==5~4,
                                      food_pricing_ranking==6~3,
                                      food_pricing_ranking==7~2,
                                      food_pricing_ranking==8~1)) %>%
  mutate(operating_costs_score=case_when(operating_costs_ranking==1~8,
                                         operating_costs_ranking==2~7,
                                         operating_costs_ranking==3~6,
                                         operating_costs_ranking==4~5,
                                         operating_costs_ranking==5~4,
                                         operating_costs_ranking==6~3,
                                         operating_costs_ranking==7~2,
                                         operating_costs_ranking==8~1)) %>%
  mutate(guest_experience_score=case_when(guest_experience_ranking==1~8,
                                          guest_experience_ranking==2~7,
                                          guest_experience_ranking==3~6,
                                          guest_experience_ranking==4~5,
                                          guest_experience_ranking==5~4,
                                          guest_experience_ranking==6~3,
                                          guest_experience_ranking==7~2,
                                          guest_experience_ranking==8~1)) %>%
  mutate(staff_satisfaction_score=case_when(staff_satisfaction_ranking==1~8,
                                            staff_satisfaction_ranking==2~7,
                                            staff_satisfaction_ranking==3~6,
                                            staff_satisfaction_ranking==4~5,
                                            staff_satisfaction_ranking==5~4,
                                            staff_satisfaction_ranking==6~3,
                                            staff_satisfaction_ranking==7~2,
                                            staff_satisfaction_ranking==8~1)) %>%
  mutate(campus_culture_score=case_when(campus_culture_ranking==1~8,
                                        campus_culture_ranking==2~7,
                                        campus_culture_ranking==3~6,
                                        campus_culture_ranking==4~5,
                                        campus_culture_ranking==5~4,
                                        campus_culture_ranking==6~3,
                                        campus_culture_ranking==7~2,
                                        campus_culture_ranking==8~1)) 
```

```{r}
survey_data <- survey_data %>%
  mutate(across(role,str_replace,"I consult on best practices","Advisor")) %>%
  mutate(across(role,str_replace,"I am a primary decision maker","Decision Maker")) %>%
  mutate(across(role,str_replace,"I offer feedback on existing services","Auditor")) %>%
  mutate(across(role,str_replace,"Other \\(please specify\\):","Advisor")) %>%
  select(-role_other)
```

```{r}
rank_frequencies <- survey_data %>%
  select(id,dietary_health_ranking,dietary_sustainability_ranking,institutional_sustainability_ranking,food_pricing_ranking,operating_costs_ranking,guest_experience_ranking,staff_satisfaction_ranking,campus_culture_ranking) %>%
  pivot_longer(!id,names_to="indicator",values_to="ranking") %>%
  mutate(across(indicator,str_replace,"guest_experience_ranking","Guest Dining Experience")) %>%
  mutate(across(indicator,str_replace,"dietary_health_ranking","Dietary Health")) %>%
  mutate(across(indicator,str_replace,"operating_costs_ranking","Operating Costs")) %>%
  mutate(across(indicator,str_replace,"dietary_sustainability_ranking","Sustainability of Guest Food Choices")) %>%
  mutate(across(indicator,str_replace,"food_pricing_ranking","Food Pricing")) %>%
  mutate(across(indicator,str_replace,"institutional_sustainability_ranking","Institutional Sustainability")) %>%
  mutate(across(indicator,str_replace,"campus_culture_ranking","Campus Culture")) %>%
  mutate(across(indicator,str_replace,"staff_satisfaction_ranking","Staff Satisfaction")) 
rank_frequencies %>%
  group_by(indicator) %>%
  summarise(mean_ranking=mean(ranking),sd_ranking=sd(ranking)) %>%
  arrange(mean_ranking)
```

```{r}
score_frequencies <- survey_data %>%
  select(id,dietary_health_score,dietary_sustainability_score,institutional_sustainability_score,food_pricing_score,operating_costs_score,guest_experience_score,staff_satisfaction_score,campus_culture_score) %>%
  pivot_longer(!id,names_to="indicator",values_to="score") %>%
  mutate(across(indicator,str_replace,"guest_experience_score","Guest Dining Experience")) %>%
  mutate(across(indicator,str_replace,"dietary_health_score","Dietary Health")) %>%
  mutate(across(indicator,str_replace,"operating_costs_score","Operating Costs")) %>%
  mutate(across(indicator,str_replace,"dietary_sustainability_score","Sustainability of Guest Food Choices")) %>%
  mutate(across(indicator,str_replace,"food_pricing_score","Food Pricing")) %>%
  mutate(across(indicator,str_replace,"institutional_sustainability_score","Institutional Sustainability")) %>%
  mutate(across(indicator,str_replace,"campus_culture_score","Campus Culture")) %>%
  mutate(across(indicator,str_replace,"staff_satisfaction_score","Staff Satisfaction"))
score_frequencies %>%
  group_by(indicator) %>%
  summarise(mean_score=mean(score),sd_score=sd(score)) %>%
  arrange(desc(mean_score))
```

```{r}
score_aov <- aov(score~indicator,data=score_frequencies)
summary(score_aov)
```

```{r}
TukeyHSD(score_aov)
```

guest_experience_score-food_pricing_score                       0.0228131
guest_experience_score-dietary_sustainability_score             0.0384822
institutional_sustainability_score-guest_experience_score       0.0016525
guest_experience_score-campus_culture_score                     0.0008360
staff_satisfaction_score-guest_experience_score                 0.0002535

```{r}
score_frequencies %>%
  group_by(indicator) %>%
  summarise(mean_score=mean(score),sd_score=sd(score)) %>%
  arrange(desc(mean_score)) %>%
  ggplot(aes(x=fct_reorder(indicator,mean_score),y=mean_score,fill=fct_reorder(indicator,mean_score))) + 
  geom_col(linewidth=0.3) + 
  geom_errorbar(aes(ymin=mean_score-sd_score,ymax=mean_score+sd_score),color="black",width=0.2,linewidth=0.3) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Staff Satisfaction")),color="black",size=0.25,annotation="***",y_position=10) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Campus Culture")),color="black",size=0.25,annotation="***",y_position=9.5) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Institutional Sustainability")),color="black",size=0.25,annotation="**",y_position=9) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Food Pricing")),color="black",size=0.25,annotation="*",y_position=8.5) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Sustainability of Guest Food Choices")),color="black",size=0.25,annotation="*",y_position=8) +
  scale_fill_viridis_d(option="mako") +
  xlab("") + 
  ylab("Mean Summary Score") +
  labs(caption="F-value: 4.81 (3sf); p-value < 0.001") + 
  coord_flip() +
  theme(legend.position="none",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```
need to put anova value in caption - could also consider boxplot/violin plot


```{r}
summary_score_plot <- score_frequencies %>%
  ggplot(aes(x=fct_reorder(indicator,score,.fun="mean"),y=score,fill=fct_reorder(indicator,score,.fun="mean"),color=fct_reorder(indicator,score,.fun="mean"))) + 
  geom_boxplot(outlier.shape=NA,color="black",size=0.25,alpha=0.8) +
   stat_summary(fun.y=mean,geom="point",shape=20,size=2,color="black",fill="white") +
  geom_signif(comparisons=list(c("Guest Dining Experience","Staff Satisfaction")),color="black",size=0.25,annotation="***",y_position=10) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Campus Culture")),color="black",size=0.25,annotation="***",y_position=9.5) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Institutional Sustainability")),color="black",size=0.25,annotation="**",y_position=9) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Food Pricing")),color="black",size=0.25,annotation="*",y_position=8.5) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Sustainability of Guest Food Choices")),color="black",size=0.25,annotation="*",y_position=8) +
  scale_fill_viridis_d(option="mako") +
  scale_color_viridis_d(option="mako",alpha=1) +
  xlab("") + 
  ylab("Mean Summary Score") + 
  labs(caption="F-value: 4.81 (3sf); p-value < 0.001") + 
  coord_flip() +
  theme(aspect.ratio=0.8,legend.position="none",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```


percent time each was ranked first 

```{r}
score_frequencies %>%
  group_by(indicator) %>%
  summarise(mean_score=mean(score),sd_score=sd(score)) %>%
  arrange(desc(mean_score)) 
```

```{r}
first_choice_frequencies <- score_frequencies %>%
  mutate(first_choice=case_when(indicator=="Guest Dining Experience"&score==8~1,
                                indicator=="Dietary Health"&score==8~1,
                                indicator=="Operating Costs"&score==8~1,
                                indicator=="Sustainability of Guest Food Choices"&score==8~1,
                                indicator=="Food Pricing"&score==8~1,
                                indicator=="Institutional Sustainability"&score==8~1,
                                indicator=="Campus Culture"&score==8~1,
                                indicator=="Staff Satisfaction"&score==8~1)) %>%
  mutate(first_choice=ifelse(is.na(first_choice),0,first_choice)) %>%
  group_by(indicator) %>%
  summarise(first_choice_frequency=sum(first_choice)) %>%
  arrange(desc(first_choice_frequency))
first_choice_frequencies
```


```{r}
first_choice_contingency_table <- first_choice_frequencies %>%
  rename(Initial=first_choice_frequency) %>%
  mutate(Noninitial=32-Initial)
first_choice_contingency_table
```

```{r}
first_choice_contingency_table <- as.table(rbind(c(9,5,5,4,4,3,2,0),c(23,27,27,28,28,29,30,32)))
dimnames(first_choice_contingency_table) <- list(dichotomy=c("Initial","Noninitial"),
                                                 indicators=c("Guest Dining Experience","Dietary Health","Institutional Sustainability","Campus Culture","Operating Costs","Food Pricing","Staff Satisfaction","Sustainability of Guest Food Choices"))
first_choice_chisq_test <- chisq.test(first_choice_contingency_table)
print(first_choice_chisq_test)
```
No significant association between the type of indicator and its likelihood of being ranked first

```{r}
first_choice_observed_counts <- first_choice_chisq_test$observed
print(first_choice_chisq_test)
```

```{r}
first_choice_expected_counts <- first_choice_chisq_test$expected
print(round(first_choice_expected_counts,2))
```

```{r}
first_choice_pearson_residuals <- first_choice_chisq_test$residuals
print(round(first_choice_pearson_residuals,2))
```

```{r}
first_choice_contributions <- (first_choice_observed_counts-first_choice_expected_counts)^2/first_choice_expected_counts
first_choice_total_chi_square <- first_choice_chisq_test$statistic
first_choice_percentage_contributions <- 100*first_choice_contributions/first_choice_total_chi_square
print("Percentage Contributions:")
```

```{r}
print(round(first_choice_percentage_contributions,2))
```

```{r}
pheatmap(first_choice_percentage_contributions,display_numbers=TRUE,cluster_rows=FALSE,cluster_cols=FALSE,main="Percentage Contributions to Chi-Square Statistic")
```

```{r}
first_choice_contingency_table <- first_choice_frequencies %>%
  rename(Initial=first_choice_frequency) %>%
  mutate(Noninitial=32-Initial) %>%
  pivot_longer(!indicator,names_to="selection",values_to="frequency") %>%
  mutate(contribution=case_when(indicator=="Guest Dining Experience"&selection=="Initial"~45.57,
    indicator=="Guest Dining Experience"&selection=="Noninitial"~6.51,
    indicator=="Dietary Health"&selection=="Initial"~1.82,
    indicator=="Dietary Health"&selection=="Noninitial"~0.26,
    indicator=="Institutional Sustainability"&selection=="Initial"~1.82,
    indicator=="Institutional Sustainability"&selection=="Noninitial"~0.26,
    indicator=="Campus Culture"&selection=="Initial"~0,
    indicator=="Campus Culture"&selection=="Noninitial"~0,
    indicator=="Operating Costs"&selection=="Initial"~0,
    indicator=="Operating Costs"&selection=="Noninitial"~0,
    indicator=="Food Pricing"&selection=="Initial"~1.82,
    indicator=="Food Pricing"&selection=="Noninitial"~0.26,
    indicator=="Staff Satisfaction"&selection=="Initial"~7.29,
    indicator=="Staff Satisfaction"&selection=="Noninitial"~1.04,
    indicator=="Sustainability of Guest Food Choices"&selection=="Initial"~29.17,
    indicator=="Sustainability of Guest Food Choices"&selection=="Noninitial"~4.17)) %>%
  mutate(label_y=case_when(selection=="Initial"~34,
                           selection=="Noninitial"~-2))
first_choice_contingency_table
```

```{r}
first_choice_frequency_plot <- ggplot(first_choice_contingency_table[order(first_choice_contingency_table$selection,decreasing=T),],aes(x=indicator,y=frequency,fill=factor(selection,levels=c("Noninitial","Initial")),color=factor(selection,levels=c("Noninitial","Initial")))) + 
  geom_col(alpha=0.9) +
  geom_text(aes(y=label_y,label=paste(format(contribution,nsmall=2),"%")),color="black",size=3) +
  geom_signif(comparisons=list(c("Guest Dining Experience","Sustainability of Guest Food Choices")),color="black",size=0.25,annotation="n.s.",y_position=34,tip_length=0.02,vjust=0) +
  xlab("Accessory Indicator") +
  ylab("Frequency") +
  scale_fill_manual(values=c("slateblue4","mediumaquamarine")) +
  scale_color_manual(values=c("slateblue4","mediumaquamarine")) +
  scale_x_discrete(limits=c("Sustainability of Guest Food Choices","Staff Satisfaction","Food Pricing","Operating Costs","Campus Culture","Institutional Sustainability","Dietary Health","Guest Dining Experience")) +
  scale_y_continuous(breaks=c(0,8,16,24,32)) +
  guides(fill=guide_legend(title="Mode"),color=guide_legend(title="Mode")) +
  labs(caption="X-squared: 13.7 (3sf); p-value = 0.056") + 
  theme(aspect.ratio=0.4,legend.position="right",panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
preliminary_indicator_rankings <- 
ggarrange(first_choice_frequency_plot,summary_score_plot,
          nrow=2,
          labels=c("A","B"))
ggsave(filename="preliminary_indicator_rankings.png",plot=preliminary_indicator_rankings,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=35,height=28,units="cm",dpi=150,limitsize=TRUE)
preliminary_indicator_rankings
```


```{r}
survey_data %>% mutate(dietary_sustainability_over_dietary_health=case_when(dietary_sustainability_ranking<dietary_health_ranking ~ 1,
                                                                                   dietary_sustainability_ranking>dietary_health_ranking ~ 0)) %>%
  summarise(dietary_sustainability_over_dietary_health_sum=sum(dietary_sustainability_over_dietary_health))
```

