---
title: "Cleaning Script"
output: github_document
date: "Last Updated: February 12, 2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Loading

```{r}
library(tidyverse)
library(ggpubr)
library(ggsignif)
library(maps)
library(sf)
library(rnaturalearth)
library(rnaturalearthhires)
```

## Data Loading 

```{r}
survey_data <- read.csv("/Users/kenjinchang/github/stakeholder-analysis/data/parent-files/survey-data.csv")
extraction_data <- read.csv("/Users/kenjinchang/github/stakeholder-analysis/data/parent-files/extraction-data.csv")
```

## Data Cleaning: Scoping Review

Below, we list, operationalize, and—where applicable—provide the input range for each of the 42 originally extracted variables:

* `study_id`: the unique numeral identifier assigned to each independently eligible study included within our scoping review (1-116).
* `study`: the parenthetical, in-text citation for each independently eligible study's corresponding record of reference. 
* `study_no`: the assigned number specifying the order in which the independently eligible study appears within the corresponding record of reference.
* `study_count`: the total number of independently eligible studies appearing within the corresponding record of reference.
* `doi`: the handle, or digital object identifier (DOI), assigned to each independently eligible study's corresponding record of reference.
* `pub_year`: the calendar year when each independently eligible study's corresponding record of reference was published (2001-2024).
* `pub_title`: the given title for each independently eligible study's corresponding record of reference.
* `pub_journal`: the publishing journal of each independently eligible study's record of reference.
* `university_list`: the complete list of treatment-receiving universities participating in the independently eligible study.
* `university_count`: the total number of treatment-receiving universities participating in the independently eligible study.
* `investigation_cat`: the scale of the independently eligible study's investigation (single-site for study's localized to one treatment-receiving university or multi-site for study's implemented across multiple treatment-receiving universities).
* `nation_list`: a duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the ISO (International Organization for Standardization) countries in which they are located.
* `nation_list_count`: the total number of unique and duplicate ISO countries associated with the participating treatment-receiving universities mentioned in each study.
* `nation_var`: a non-duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the ISO countries in which they are located.
* `nation_var_count`: the total number of unique ISO countries associated with the participating treatment-receiving universities mentioned in each study.
* `us_state_list`: a conditional, duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.S. state in which they are located.
* `us_state_list_count`: the total number of unique and duplicate U.S. states associated with the participating treatment-receiving universities mentioned in each study.
* `us_state_var`: a conditional, non-duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.S. states in which they are located.
* `us_state_var_count`: the total number of unique U.S. states associated with the participating treatment-receiving universities mentioned in each study. 
* `uk_country_list`: a conditional, duplicate-allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.K. country in which they are located.
* `uk_country_list_count`: the total number of unique and duplicate U.K. countries associated with the participating treatment-receiving universities mentioned each study.
* `uk_country_var`: a conditional, non-duplicate allowing list pairing the participating treatment-receiving universities mentioned in each study with the U.K. countries in which they are located.
* `uk_country_var_count`: the total number of unique U.K. countries associated with the participating treatment-receiving universities mentioned in each study.
* `strategy_list`: a duplicate-allowing list pairing the reported intervention components mentioned in each study with the specific behavioral strategies being leveraged. 
* `approach_cat`: the diagnosed behavioral approach associated with each study, based on the strategies mapping on to each study's reported intervention components.
* `target_list`: a duplicate-allowing list pairing the reported intervention components mentioned in each study with the specific socio-ecological tiers being targeted.
* `breadth_cat`: the diagnosed breadth of change associated each study, based on the socio-ecological tiers mapping on to each study's reported intervention components.
* `design`: the  research design of the included study, as determined by the nature of comparison being made (between, within, or between and within).
* `principal_indicator_list`: a duplicate-allowing list outlining the primary outcome measures being used to document changes to food selection or food service in response to the study's reported intervention. 
* `principal_indicator_list_count`: the total number of unique and duplicate primary outcome measures being
* `principal_indicator_var`:
* `principal_indicator_var_count`:
* `accessory_indicator_list`:
* `accessory_indicator_list_count`:
* `accessory_indicator_var`:
* `accessory_indicator_var_count`:
* `qualifying_indicator_list`:
* `qualifying_indicator_list_count`:
* `qualifying_indicator_var`:
* `qualifying_indicator_var_count`:
* `spillover_monitoring_list`:
* `spillover_monitoring_list_count`:
* `spillover_monitoring_var`:
* `spillover_monitoring_var_count`:
* `intention_behavior_monitoring`:

### Time

```{r}
temporal_frequencies <- extraction_data %>%
  select(pub_year,university_count) %>%
  drop_na() %>%
  mutate(count=case_when(university_count>=1~1)) %>%
  group_by(pub_year) %>%
  summarise(frequency=sum(count)) %>%
  mutate(cumulative_frequency=cumsum(frequency)) %>%
  add_row(pub_year=2000,frequency=0) %>%
  add_row(pub_year=2002,frequency=0) %>%
  add_row(pub_year=2003,frequency=0) %>%
  add_row(pub_year=2004,frequency=0) %>%
  add_row(pub_year=2007,frequency=0) %>%
  add_row(pub_year=2008,frequency=0) %>%
  add_row(pub_year=2010,frequency=0) %>%
  arrange(pub_year) %>%
  mutate(cumulative_frequency=cumsum(frequency)) 
temporal_frequencies
```

```{r}
exponential_fit <- temporal_frequencies %>%
  slice(-1)
exponential_model <- lm(log(cumulative_frequency)~pub_year,data=exponential_fit)
summary(exponential_model)
```

```{r}
temporal_frequencies_plot <- temporal_frequencies %>%
  ggplot(aes(x=pub_year,y=frequency,color=frequency,fill=frequency)) + 
  geom_col() +
  scale_fill_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  scale_color_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  xlab("Publication Year") + 
  ylab("Frequency") + 
  scale_y_continuous(limits=c(0,120)) +
  scale_x_continuous(breaks=c(2000,2004,2008,2012,2016,2020,2024),limits=c(2000,2025)) +
  labs(caption="   ") + 
  theme(legend.position="none",legend.justification="center",legend.box.spacing=unit(0,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
temporal_cumulative_frequencies_plot <- temporal_frequencies %>%
  ggplot(aes(x=pub_year,y=cumulative_frequency,color=cumulative_frequency,fill=cumulative_frequency)) +
  scale_fill_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  scale_color_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  geom_col() + 
  xlab("Publication Year") + 
  ylab("Cumulative Frequency") + 
  scale_y_continuous(limits=c(0,120)) +
  scale_x_continuous(breaks=c(2000,2004,2008,2012,2016,2020,2024),limits=c(2000,2025)) +
  labs(caption="Adjusted R-Squared: 0.985 (3sf)") + 
  theme(legend.title.position="none",legend.position="none",legend.justification="center",legend.box.spacing=unit(0,"pt"),legend.key.width=unit(50,"pt"),legend.key.height=unit(7.5,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
temporal_plots <- ggarrange(temporal_frequencies_plot,temporal_cumulative_frequencies_plot,
          nrow=2,
          labels=c("A","B"))
ggsave(filename="publication-rate.png",plot=temporal_plots,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=30,height=20,units="cm",dpi=150,limitsize=TRUE)
temporal_plots
```

### Place

```{r}
global_shapefile <- map_data("world")
global_shapefile <- global_shapefile %>% 
  rename(country=region) %>%
  mutate(country=case_when(country=="Macedonia"~"North Macedonia",
                           country=="Ivory Coast"~"Cote d'Ivoire",
                           country=="Democratic Republic of the Congo"~"Congo, Dem. Rep.",
                           country=="Republic of Congo"~"Congo, Rep.",
                           country=="UK"~"United Kingdom",
                           country=="USA"~"United States",
                           country=="Laos"~"Lao",
                           country=="Slovakia"~"Slovak Republic",
                           country=="Saint Lucia"~"St. Lucia",
                           country=="Kyrgyzstan"~"Krygyz Republic",
                           country=="Micronesia"~"Micronesia, Fed. Sts.",
                           country=="Swaziland"~"Eswatini",
                           country=="Virgin Islands"~"Virgin Islands (U.S.)",
                        TRUE~country))
island_nations <- c("Antigua","Barbuda","Nevis", 
                 "Saint Kitts","Trinidad",
                 "Tobago","Grenadines","Saint Vincent")
island_nations_match <- global_shapefile %>% 
  filter(country %in% island_nations)
ant_bar <- c(137,138 )
kit_nev <- c(930,931)
tri_tog <- c(1425,1426)
vin_gre <- c(1575,1576,1577)
island_nation_names <- c("Antigua and Barbuda","St. Kitts and Nevis","Trinidad and Tobago","St. Vincent and the Grenadines")
island_nations_match <- island_nations_match %>% 
  mutate(country=case_when(group %in% ant_bar~"Antigua and Barbuda",
                           group %in% kit_nev~"St. Kitts and Nevis",
                           group %in% tri_tog~"Trinidad and Tobago",
                           group %in% vin_gre~"St. Vincent and the Grenadines")) %>% 
  tibble()
global_shapefile <- global_shapefile %>%
  filter(!country %in% island_nation_names)
global_shapefile <- global_shapefile %>% 
  bind_rows(island_nations_match) %>%
  arrange(country) %>%
  tibble()
sra_names <- c("Hong Kong","Macao")
hk_mc <- global_shapefile %>% 
  filter(subregion %in% sra_names)
hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion=="Hong Kong"~"Hong Kong, China",
                             subregion=="Macao"~"Macao, China"))
global_shapefile <- global_shapefile %>%
  filter(!subregion %in% sra_names)
global_shapefile <- global_shapefile %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

```{r}
spatial_frequencies <- extraction_data %>%
  select(nation_var,nation_var_count) %>%
  rename(country=nation_var) %>%
  mutate(across(country,str_replace,"USA","United States")) %>%
  mutate(across(country,str_replace,"UK","United Kingdom")) %>%
  group_by(country) %>%
  summarise(frequency=sum(nation_var_count)) %>%
  arrange(desc(frequency))
spatial_frequencies
```

```{r}
spatial_frequencies %>%
  summarise(sum(frequency))
```
scale_fill_gradient(low='white', high='grey20', limits=c(1, 10))

scale_fill_gradient(low="lavender",high="slateblue4",na.value="white",name="Intervention-Receiving Institutions",guide=guide_colourbar(reverse=FALSE,title.position="top",title.hjust=0.5,limits=c(1,116))) +

```{r}
crs_robin <- "+proj=robin +lat_0=0 +lon_0=0 +x0=0 +y0=0"
```


```{r}
spatial_frequencies_joined <- left_join(global_shapefile,spatial_frequencies,by="country")
national_frequencies <- spatial_frequencies_joined %>%
  ggplot(aes(x=long,y=lat,fill=frequency,group=group)) + 
  geom_polygon(color="black",linewidth=0.125,alpha=0.60) +
  scale_fill_gradient(low="lavender",high="slateblue4",na.value="white",limits=c(1,55)) +
  coord_sf(crs=crs_robin) +
  xlab("") + 
  ylab("") +
  scale_y_continuous(limits=c(-55,85)) +
  labs(caption="") +
  theme(legend.key.width=unit(3,"lines"),legend.position="none",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

scale_fill_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +
  scale_color_gradient(name="Count",low="lavender",high="slateblue4",limits=c(1,116),na.value="lavender",breaks=c(1,29,58,87,116)) +

```{r}
usa_shapefile <- map_data("county") %>%
  rename(state=region)
```

```{r}
state_frequencies <- extraction_data %>%
  select(study,us_state_var) %>%
  separate_longer_delim(c(us_state_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(us_state_var) %>%
  summarise(frequency=sum(count)) %>%
  arrange(desc(frequency)) %>%
  mutate(us_state_var=tolower(us_state_var)) %>%
  rename(state=us_state_var) %>%
  drop_na()
state_frequencies 
```

```{r}
state_frequencies %>% summarise(sum(frequency))
```

```{r}
state_frequencies_joined <- left_join(usa_shapefile,state_frequencies,by="state")
```

```{r}
usa_frequencies <- state_frequencies_joined %>%
  ggplot(aes(x=long,y=lat,fill=frequency,group=group)) + 
  geom_polygon(color="black",linewidth=0.125) +
  scale_fill_gradient(low="lavender",high="slateblue4",na.value="white",limits=c(1,55)) +
  xlab("") + 
  ylab("") +
  labs(caption="") +
  coord_map("albers",lat0=45.5,lat1=29.5) +
  theme(legend.key.width=unit(3,"lines"),legend.position="none",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
subnational_frequencies <- extraction_data %>%
  select(uk_country_var,uk_country_var_count) %>%
  rename(subregion=uk_country_var) %>%
  separate_longer_delim(c(subregion,uk_country_var_count),delim=";") %>%
  mutate(uk_country_var_count=as.numeric(uk_country_var_count)) %>%
  group_by(subregion) %>%
  summarise(frequency=sum(uk_country_var_count)) %>%
  arrange(desc(frequency)) %>%
  mutate(across("subregion",str_replace,"England","Great Britain")) %>%
  drop_na()
subnational_frequencies
```

```{r}
uk_shapefile <- ne_states(country="united kingdom",returnclass="sf")
```

```{r}
subnational_frequencies <- subnational_frequencies %>%
  mutate(across('subregion',str_replace,"Great Britain","England")) %>%
  rename(geonunit=subregion)
subnational_frequencies
```

```{r}
subnational_frequencies_joined <- left_join(uk_shapefile,subnational_frequencies,by="geonunit")
```

```{r}
uk_frequencies <- subnational_frequencies_joined %>%
ggplot(aes(fill=frequency,group=geonunit)) + 
  geom_sf(aes(fill=frequency),color="black",linewidth=0.125) +
  scale_fill_gradient(low="lavender",high="slateblue4",na.value="white",limits=c(1,55)) +
  theme(legend.key.width=unit(3,"lines"),legend.position="none",legend.justification="center",legend.box.spacing=unit(-15,"pt"),legend.key.size=unit(10,"pt"),panel.grid=element_blank(),panel.background=element_rect(fill="white"),panel.border=element_rect(fill=NA),axis.text=element_blank(),axis.ticks=element_blank(),legend.title=element_text(size=10),legend.text=element_text(size=10),plot.title=element_text(size=10))
```

```{r}
subnational_frequency_choros <- ggarrange(usa_frequencies,uk_frequencies,
                                         ncol=2,
                                         labels=c("B","C"))
national_frequency_choros <- ggarrange(national_frequencies,
                                       labels="A")
```


```{r}
spatial_plots <- ggarrange(national_frequency_choros,subnational_frequency_choros,
          nrow=2)
ggsave(filename="publication-distribution.png",plot=spatial_plots,path="/Users/kenjinchang/github/stakeholder-analysis/figures",width=30,height=20,units="cm",dpi=150,limitsize=TRUE)
spatial_plots
```

### Primary Performance Indicators

```{r}
ppi_frequencies <- extraction_data %>%
  select(study,principal_indicator_var) %>%
  separate_longer_delim(c(principal_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(principal_indicator_var) %>%
  summarise(frequency=sum(count))
ppi_frequencies 
```

```{r}
extraction_data %>%
  select(principal_indicator_var) %>%
  str_count("Self-Reported Food Choice")
```

```{r}
extraction_data %>%
  select(principal_indicator_var) %>%
  str_count("Observed Food Choice")
```

```{r}
extraction_data %>%
  select(principal_indicator_var) %>%
  str_count("Intended Food Choice")
```

```{r}
extraction_data %>%
  select(principal_indicator_var) %>%
  str_count("Observed Food Service")
```

### Accessory Performance Indicators

```{r}
api_frequencies <- extraction_data %>%
  select(study,accessory_indicator_var) %>%
  separate_longer_delim(c(accessory_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(accessory_indicator_var) %>%
  summarise(frequency=sum(count))
api_frequencies
```


not sure why this isn't collapsing correctly


variety

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Campus Culture")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Dietary Health")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Operating Costs")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Sustainability of Guest Food Choices")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Guest Dining Experience")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Food Pricing")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Institutional Sustainability")
```

```{r}
extraction_data %>%
  select(accessory_indicator_var) %>%
  str_count("Staff Satisfaction")
```

list

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Campus Culture")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Dietary Health")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Operating Costs")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Sustainability of Guest Food Choices")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Guest Dining Experience")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Food Pricing")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Institutional Sustainability")
```

```{r}
extraction_data %>%
  select(accessory_indicator_list) %>%
  str_count("Staff Satisfaction")
```

### Performance Qualifiers 

api_frequencies <- extraction_data %>%
  select(study,accessory_indicator_var) %>%
  separate_longer_delim(c(accessory_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(accessory_indicator_var) %>%
  summarise(frequency=sum(count))
api_frequencies
```{r}
qpi_frequencies <- extraction_data %>%
  select(study,qualifying_indicator_var) %>%
  separate_longer_delim(c(qualifying_indicator_var),delim=";") %>%
  add_column(count=1) %>%
  group_by(qualifying_indicator_var) %>%
  summarise(frequency=sum(count))
qpi_frequencies
```

```{r}
extraction_data %>%
  select(qualifying_indicator_var) %>%
  str_count("Demographics")
```

```{r}
extraction_data %>%
  select(qualifying_indicator_var) %>%
  str_count("Lifestyle")
```

```{r}
extraction_data %>%
  select(qualifying_indicator_var) %>%
  str_count("Program Reception")
```

```{r}
extraction_data %>%
  select(qualifying_indicator_var) %>%
  str_count("Situational")
```

### Gap Monitoring

#### Spillover 

#### Intention-Behavior Asymmetries



## Data Cleaning: Stakeholder Analysis


